Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Legger til toc.
Figure sizing.

---
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

@@

```{r, echo=FALSE}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

@@

```{r, echo=FALSE}
knitr::include_graphics("Images/info_kreft.png")
knitr::include_graphics("Images/regnskapssti.png")
```

>>>>

---
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "`r Sys.Date()`"
output:
  pdf_document: 
    toc: true
  html_document: default
---

@@

```{r, echo=FALSE, out.width="70%"}
knitr::include_graphics("Images/lagret_tekst.png") # må finne ut av hvordan vi deler disse bildene

@@

```{r, echo=FALSE, out.width="70%"}
knitr::include_graphics("Images/info_kreft.png")
```

```{r, echo=FALSE, out.width="100%"}
knitr::include_graphics("Images/regnskapssti.png")
```
